Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-05 doc/prelim/presentation/prelim_presentation.tex
removing sequential monte carlo slide
adding acknowledgements slide
updating acks slide

  \begin{itemize}
  \item Neumann-Ulam methods bound by the Central Limit Theorem
  \item Build on Halton's 1962 iterative residual method
  \item Adjoint Neumann-Ulam solver computes the correction
  \item Decouples MC error from solution error, exponential convergence
  \item Demonstrated by Evans to be competitive with Krylov methods
  \end{itemize}

@@

>>>>

  \begin{itemize}
  \item Neumann-Ulam methods bound by the Central Limit Theorem
  \item Build on Halton's 1962 Sequential Monte Carlo method
  \item Adjoint Neumann-Ulam solver computes the correction
  \item Decouples MC error from solution error, exponential convergence
  \item Demonstrated by Evans to be competitive with Krylov methods
  \end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Acknowledgements}

  Thanks to...\footnote{This work was performed under
        appointment to the Nuclear Regulatory Commission Fellowship
        program at the University of Wisconsin - Madison Department of
        Engineering Physics.}

  \begin{itemize}
  \item Paul Wilson
  \item Tom Evans
  \item ORNL and SNL
  \end{itemize}
